\section{Introduction}
The satisfiability problem (SAT) is an NP-complete problem
\parencite{cook_1971}. A SAT problem consists of a set of Boolean variables
$x_1, \cdots, x_n$ and a Boolean formula $f: \mathbb{B}^n \rightarrow \mathbb{B}=\{0, 1\}$. The
question is whether an assignment $x=(x_1, \cdots, x_n)$ exists such that
$f(x)=1$ \parencite{gottlieb_marchiori_rossi_2002}. A wide range of problems can be
expressed as SAT problems. This includes verification, planning, scheduling
and combinatorial design \parencite{biere2009handbook}. Hence, a SAT solver has been a
general purpose platform for solving various real-world problems and has
obvious importance.

There are two types of SAT solver technologies: complete methods and
incomplete methods. Complete methods can guarantee to eventually report a
satisfying assignment or prove not satisfiable, long enough time.
Complete methods have an exponential time complexity if P
$\neq$ NP. On the other hand, incomplete methods have no such
guarantee and generally use stochastic local search \parencite{gomes_kautz_sabharwal_selman_2008}. In
many cases where the problem does not require a definitive answer, incomplete
methods could outperform complete methods in terms of both speed and memory
usage.

Genetic algorithms (GAs) are incomplete methods that have been applied to many
NP-complete problems, including SAT \parencite{gottlieb_marchiori_rossi_2002}. However, results
suggest that classical GAs may not outperform local search algorithms
\parencite{de1989using}. Nevertheless, recent results show that GAs can yield
good results if combined with other methods \parencite{gottlieb_marchiori_rossi_2002}.

This paper proposes a genetic algorithm: GNTSAT, which is based on WalkSAT
\parencite{selman1994noise} and outperforms WalkSAT in many benchmark instances. WalkSAT is a local search-based method and it would restart the searching after a maximum searching steps without retaining any results.
This paper introduces the GNTSAT algorithm, makes performance evaluations
based on benchmarks, and discusses the possible reasons for the performance
difference and their implications.
