	\section{Methods}
	\subsection{The algorithm}
	The population is initialized randomly.  In each iteration, first using tournament to select some best individuals according to fitness.
	Then crossover are performed on two individuals among the bests. Each
	generated child is improved individually using local search, and then new individuals are inserted to the population to replace the old
	individuals under some conditions. Iterate the process until a solution is found.
	Our SAT Solver is described in detail as Algorithm \ref{alg:sat}.
	\begin{algorithm}
	    \SetAlgoLined
	    \caption{SAT Solver Algorithm}
	    \label{alg:sat} 
	    \KwData{population}
	    \KwResult{a solution for the instance}
	    \BlankLine
	    \While{true}{
	      \If{a solution is found}{
	            return the solution\;
	        }   
	      select some best individuals\;
	      randomly choose two individuals among the bests for crossover\;
	    \For{each each generated child}{
	      local search\;
	      \If{fitness (improved child) > fitness (the oldest individual)}{
	        insert the new child\;
	        remove the oldest individual\;
	    }
	    }
	    }
	  \end{algorithm}
	
	\subsubsection{Representation}
	A candidate solution is a string of bits whose length equals to the number of
	variables of the considered problem instance. Every variable is associated to
	one bit. This is the most obvious way to represent a solution candidate. It
	also makes mutation and crossover operations computationally efficient. The
	most successful evolutionary algorithms for SAT also uses representation
	\parencite{gottlieb_marchiori_rossi_2002}. Hence the bit string representation is a reasonable
	starting point.
	
	\subsubsection{Fitness function}
	The fitness value is equivalent to the number of satisfied clauses of the
	individual.
	\begin{equation*}
		\mathit{fitness}(x) = \sum_{i=1}^m c_i(x)
	\end{equation*}
	where $c_i(x)$ is the truth value of the $i$th
	clause, and $m$ is the number of clauses.
	
	\subsubsection{Selection operation}
	GNTSAT uses a modified version of tournament selection. First, a certain
	number of individuals are randomly select to participate in the tournament.
	The participating individuals are ranked according to fitness. The most fit
	individuals will be selected and stored in a best individuals pool. The two
	parents will be selected randomly from this pool.
	
	\subsubsection{Crossover operators}
	The main goal of the crossover operator in GNTSAT is to create potentially
	promising new individuals. Using the selected parents, there are many ways for
	them to crossover, and we consider 5 types: CC (Corrective Clause) Crossover,
	F\&F (Fleurent and Ferland) Crossover, Uniform Crossover, One-point Crossover
	and Two-point Crossover. We will introduce them respectively below.
	\begin{algorithm}
			\SetAlgoLined
			\KwData{two parents $X$ and $Y$}
			\KwResult{one child $Z$}
			\BlankLine
				all the bits of child $Z$ take the values of parent $X$ or parent $Y$ with the equal probability\;
			\For{each clauses c such that $ \neg sat(X,c) \wedge \neg sat(Y,c)$}{
				\For{all positions $i$ such that the variable $x_{i}$ appears in c}{
				Compute $ \sigma = improvement(X, i) + improvement(Y, i)$ \;
				}{
				Set $Z\vert k = flip(X\vert k)$ where $k$ is the position such that $\sigma$ is maximum\;
				}
			}
			\caption{Corrective Clause Algorithm}
			\label{alg:cc} 
			\end{algorithm}
			\begin{algorithm}
				\SetAlgoLined
				\caption{Fleurent and Ferland Crossover}
				\label{alg:ff} 
				\KwData{two parents $X$ and $Y$}
				\KwResult{one child $Z$}
				\BlankLine
				  all the bits of child $Z$ take the values of parent $X$ or parent $Y$ with the equal probability\;
				\For{each clauses c such that $ sat(X,c) \wedge \neg sat(Y,c)$ (resp. $\neg sat(X,c) \wedge sat(Y,c))$}{
				  \For{all positions i such that the variable $x_{i}$ appears in c}{
					$Z\vert i = X \vert i$ (resp. $Z\vert i = Y \vert i$)\;
				  }{
				  Set $Z\vert k = flip(X\vert k)$ where $k$ is the position such that $\sigma$ is maximum\;
				  }
				}
			  \end{algorithm}
			  \begin{algorithm}
				\SetAlgoLined
				\caption{Uniform Crossover}
				\label{alg:uniform} 
				\KwData{two parents $X$ and $Y$}
				\KwResult{one child $Z$}
				\BlankLine
				\For{each bit $x$}{
				  $Z\vert x = X\vert x$ or $Z\vert x = Y\vert x$ with equal possibility\;
				}
			  \end{algorithm}
			  \begin{algorithm}
				\SetAlgoLined
				\caption{One-point Crossover}
				\label{alg:onepoint} 
				\KwData{two parents $X$ and $Y$ }
				\KwResult{two children $Z_1$ and $Z_2$}
				\BlankLine
				\For{each bit $x$ where its position is less than the pivot point}{
				  $Z_1\vert x = X\vert x$\;
				  $Z_2\vert x = Y\vert x$\;
				}
				\For{each bit x where its position is larger than the pivot point}{
				  $Z_1\vert x = Y\vert x$\;
				  $Z_2\vert x = Y\vert x$\;
				}
			  \end{algorithm}
	\begin{itemize}
		\item
		      CC (Corrective Clause) Crossover: For each clause c that is unsatisfiable for
		      both parent X and parent Y solutions and for each variables that appears in
		      clause c, find the bit position using the literally absolute value
		      $i$ of the variable that produces the maximum improvement on
		      two parents guided by the improvement evaluation function. The function equals
		      to the number of false clauses which become true by flipping the
		      $ith$ bit in one of the solutions minus the number of
		      satisfied clauses which become false. Assign the flipped value applied to one
		      of the parents to the child in the bit position found, and all the bits with
		      no value of child take the value in corresponding position of parent X or
		      parent Y with the equal probability. CC crossover is illustrated in detail as Algorithm \ref{alg:cc}.
			
		\item
		      F\&F (Fleurent and Ferland) Crossover: For each clause c that is satisfiable
		      for one parent and unsatisfiable for the other parent and for each variables
		      that appears in clause c, the bits positions in the child, corresponding to
		      the literally absolute value $i$ of the variable in parents,
		      are assigned values according to the parent satisfying the identified clause.
		      All the bits with no value of the child take the value in corresponding
		      position of parent X or parent Y with the equal probability. F\&F crossover is illustrated in detail as Algorithm \ref{alg:ff}.
			  
		\item
		      Uniform Crossover: With equal probability, each bits of the child is chosen
		      from either parent. In that case, one new offspring is generated. Uniform Crossover is illustrated in detail as Algorithm \ref{alg:uniform}.
			  
		\item One-point Crossover: Randomly select one pivot point (ranging between 0 to
		      length of the bits string) and exchange the substring from that bit point till
		      the end of the string between the two individuals. In that case, two new
		      offspring individual are generated. One-point Crossover is illustrated in detail as Algorithm \ref{alg:onepoint}.
		\item
		      Two-point Crossover: Randomly pick two pivot points and the bits in between
		      the two points are swapped between the parent individuals. In that case, two
		      new offspring individual are generated. Two-point Crossover is illustrated in detail as Algorithm \ref{alg:twopoint}.
			 
	\end{itemize}
	\begin{algorithm}
				\SetAlgoLined
				\caption{Two-point Crossover}
				\label{alg:twopoint} 
				\KwData{two parents $X$ and $Y$ }
				\KwResult{two children $Z_1$ and $Z_2$}
				\BlankLine
				\For{each bit $x$ where its position is in between the two pivot points}{
				  $Z_1\vert x = X\vert x$\;
				  $Z_2\vert x = Y\vert x$\;
				}
				\For{each bit $x$ where the position is not in between the two pivot points}{
				  $Z_1\vert x = Y\vert x$\;
				  $Z_2\vert x = Y\vert x$\;
				}
			  \end{algorithm}
	
	\subsubsection{Local search}
	We implement the idea of mutation in genetic algorithm using WalkSat local search method. It's a randomized local search algorithm. WalkSat is illustrated in detail as Algorithm \ref{alg:walksat}. It attempts to determine the best move by randomly choosing a clause among those that are currently unsatisfied and selecting a variable to flip within it under some conditions. The evaluation function in deciding bits to flip here is called break-count. It equals to the number of satisfied clauses which become unsatisfied by flipping a bit. The maximum number of flips (MAX-Flips) is set to 1000 and the probability of a random move $p$ is set to 0.57 since it's the optimal noise value \parencite{SAO05}. The search stops when one solution is found.
	
	\begin{algorithm*}
	  \SetAlgoLined
	  \caption{WalkSat Local Search}
	  \label{alg:walksat} 
	  \KwData{one child $Z$ generated from the crossover above }
	  \KwResult{a solution for the instance}
	  \BlankLine
	    all the bits of child Z take the values of parent X or parent Y with the equal probability\;
	  \For{ $i \leftarrow 1$ to MAX-Flips}{
	    \If{$Z$ is a solution}{
	      return $Z$\;
	    }
	    {Clause C is randomly selected among unsatisfied clauses\;}  
	    \eIf{$\exists$ variable $c \in C$ with $\operatorname{beak-count}=0$}{
	      $v\leftarrow c$\;
	      }{
	      with probability p:
	      $v\leftarrow$ a variable x in C chosen randomly\;
	      with probability 1-p:
	      $v\leftarrow$ a variable x in C with smallest $\operatorname{beak-count}$ \;
	      }
	      {Flip $v$ in Z\;}
	  }
	\end{algorithm*}
	\subsection{Implementation}
	GNTSAT is implemented in C++. GNTSAT takes a DIMACS CNF file as input and
	output the resulting bit string if found. User could adjust parameters such as
	population size, tournament size, and crossover operator.
	
	\subsection{Performance measures}
	After all these processes to generate a solution, we compare our solver using
	different crossovers and with other existing solvers. Several runs are
	required for each benchmark instance under consideration and some measuring
	methods need to be taken for statistically meaningful and also relatively fair
	results. We take 10 runs and consider three measuring methods: SR (Success
	rate), AT (Average Time) and AFS (Average Flips to Solution). We will
	introduce them respectively below.
	
	\begin{itemize}
		\item
		      SR (Success rate): SR represents the percentage of runs where a solution has
		      been found within a time limit. Since some runs where the time to get a
		      solution is too long or the solver is stuck in the local optimal solution, we
		      use SR to measure the quality of the solver. And the maximum time we set for a
		      successful run is 120 seconds.
		\item
		      AT (Average Time): AT represents the average seconds taken in successful runs.
		\item
		      AFS (Average Flips to Solution): Relating the computational costs to the
		      number of the basic moves in the search space for a solution has become the
		      standard measure used for studying the cost of SAT algorithms
		      \parencite{Singer2000}. AFS represents the average number of bit flips needed
		      to find a solution in successful runs, which was raised by
		      \citeauthor{Voss} and used to compare EAs generating new solution
		      candidates by single bit flips \parencite{Voss}.
	\end{itemize}
